
        \documentclass[a4paper, 12pt]{article}
    \usepackage{graphicx}
    \usepackage{hyperref}
    \begin{document}

    % Title Section
    \title{\textbf{Resume}}
    \author{\textbf{Chenna Sanjana}}
    \date{}
    \maketitle

    **Option 1 (Concise):**

**Chenna Sanjana**
Hyderabad, Telangana, India | +91-XXXXXXXXXX (Add your phone number) | chenna.sanjana@email.com (Add your email address)

**Summary**

Highly motivated and results-oriented student at VNR VIGNANA JYOTHI INSTITUTE OF ENGINEERING AND TECHNOLOGY pursuing a Bachelor's degree (Specify Degree) expected to graduate in 2026. Proficient in C, C++, and Python programming languages with experience in developing a carpooling project.  Seeking opportunities to leverage technical skills and contribute to a challenging and rewarding environment.


**Skills**

* **Programming Languages:** C, C++, Python, Core Java
* **Project Management:** (Add any relevant project management skills if applicable)


**Projects**

* **Carpooling Project:** ( Briefly describe the project, highlighting key accomplishments, technologies used, and results.  Quantify achievements whenever possible.  e.g., "Developed a carpooling application using Python and Flask, resulting in a 15% reduction in estimated travel time for users.")


**Education**

* **VNR VIGNANA JYOTHI INSTITUTE OF ENGINEERING AND TECHNOLOGY, Hyderabad, Telangana, India** - Bachelor's Degree (Specify Degree, e.g., Bachelor of Technology in Computer Science), Expected Graduation: 2026


**Option 2 (More Detailed - If you have more to add):**


**Chenna Sanjana**
Hyderabad, Telangana, India | +91-XXXXXXXXXX | chenna.sanjana@email.com | [LinkedIn Profile URL (Optional)] | [GitHub Profile URL (Optional)]

**Summary**

Highly motivated and results-oriented student at VNR VIGNANA JYOTHI INSTITUTE OF ENGINEERING AND TECHNOLOGY pursuing a Bachelor of Technology in [Specify your major, e.g., Computer Science Engineering] with an expected graduation date of 2026.  Possessing a strong foundation in programming languages such as C, C++, Python, and Core Java, I am eager to apply my skills and knowledge to a challenging and innovative environment.  My experience developing a carpooling project demonstrates my ability to [mention relevant skills like problem-solving, teamwork, etc.].


**Skills**

* **Programming Languages:** C, C++, Python, Java (Core Java)
* **Software/Tools:** (List any relevant software or tools you are proficient in, e.g., Git, specific IDEs)
* **Databases:** (If you have experience with databases, list them here)
* **Project Management:** (Add any relevant project management skills if applicable)


**Projects**

* **Carpooling Project:** (Provide a more detailed description, including technologies used, your role, challenges overcome, and results. Quantify your accomplishments whenever possible. For example:  "Developed a carpooling web application using Python (Flask framework), PostgreSQL database, and HTML/CSS/JavaScript.  Successfully implemented a route optimization algorithm resulting in a 20% reduction in overall travel distance for users.  Managed the project using Agile methodologies and collaborated effectively with a team of three.")


**Education**

* **VNR VIGNANA JYOTHI INSTITUTE OF ENGINEERING AND TECHNOLOGY, Hyderabad, Telangana, India** - Bachelor of Technology in [Specify your major], Expected Graduation: 2026
* **[Add High School Information if relevant]**


**Extracurricular Activities/Certifications:** (Add any relevant information here)


Remember to replace the bracketed information with your specific details.  The more detail you provide (while keeping it concise and relevant), the stronger your resume will be.  Adding links to your GitHub or LinkedIn profile is also highly recommended.
 
   
    % Closing
    \end{document}